This is the title [Article v\versionnumber]

### 2022-02-21 manuscript/manuscript.tex
Fix a typo

\begin{abstract}
Grid inhomogeneous solvation theory (GIST) is a method to compute the free energy of hydration of a compound on a 3-dimensional grid. The high spacial resolution of the GIST output, as well as the decomposition into energy and entropy contributions, allow for highly detailed analyses on both proteins and small molecules. However, this versatility also comes with a higher entry barrier for new users.

>>>>

\begin{abstract}
Grid inhomogeneous solvation theory (GIST) is a method to compute the free energy of hydration of a compound on a 3-dimensional grid. The high spatial resolution of the GIST output, as well as the decomposition into energy and entropy contributions, allow for highly detailed analyses on both proteins and small molecules. However, this versatility also comes with a higher entry barrier for new users.
